\documentclass[12pt]{article}
\usepackage{fullpage}

\title{Postdoctoral Research Assistant \\in AI for Autonomous Systems}
\date{}
\author{Charlie Street}

\begin{document}
\maketitle
\thispagestyle{empty}

% The main evidence section
My DPhil research is focused on multi-robot coordination under temporal uncertainty, which overlaps substantially with the requirements of the advertised role.
%
Capturing temporal uncertainty requires continuous-time Markov models.
%
For example, I have used Markov automata to capture asynchronous multi-robot execution in continuous-time, extended Markov automata for non-stationary environments, and used continuous-time Markov chains to describe robot policy execution.
%
I have applied multi-robot planning solutions to effectively coordinate robots under congestion, and used multi-robot task allocation techniques assign tasks under spatiotemporal uncertainty.
%
Formal methods underpin many of the solution methods I have developed.
%
For example, I have used model checking techniques to compute distributions over robot presence in the environment, and to reason over the time and locations tasks are announced, for robots to service.
%
If I am successful in applying for this role, I intend to expand on these ideas to coordinate multi-robot systems with formal performance guarantees.

% Comms Skills
I have the strong communication skills necessary for the role.
%
This is demonstrated by my publication record in high impact venues such as IEEE T-RO and AAMAS.
%
Further, I have experience presenting my work to scientific audiences at conferences including AAMAS and IEEE MRS, as well as the general public.
%
For example, I led demonstrations of a Toyota Human Support Robot and UR-10 manipulator at the Goodwood Festival of Speed, explaining robotics concepts to a non-technical audience.
%
During my DPhil, I have had the opportunity to supervise four undergraduate projects, which will prepare me for the increased supervision responsibilities in the advertised position.
%
I have also engaged with Accenture Labs in an ongoing industrial collaboration on multi-robot warehouse logistics.

% Real Robot Deployment
In addition to my research, I have spent time integrating my work onto real robot systems.
%
In the First Fleet project, I integrated my work on congestion-aware planning onto fleets of agricultural robots aiding humans in fruit fields.
%
This required substantial software engineering to adapt my work for online settings.
%
Moreover, my work in Team ORIon has given me opportunity to deploy a service robot in domestic environments.
%
More so than First Fleet, competing in RoboCup exposed me to the challenges of integrating a robot with manipulators, speech functionality etc.

My previous work has given me many of the necessary skills required for this role, and if successful, I hope to develop them further while producing high quality research.


\end{document}