\documentclass[12pt]{article}
\usepackage{fullpage}

\title{Research Fellow - School of Computer Science}
\date{}
\author{Charlie Street}

\begin{document}
\maketitle
\thispagestyle{empty}

% The main evidence section

I am applying for this position to take the next step in my academic career, and to contribute towards an exciting project with real-world outcomes.
%
The aims of the CONVINCE project align well with my existing research.
%
My DPhil focused on multi-robot coordination under temporal uncertainty.
%
Within this, I explored models which capture robot behaviour more accurately than common formalisms such as Markov decision processes, which consider limited forms of uncertainty.
%
For example, I used Markov automata to model asynchronous multi-robot execution, extended Markov automata for non-stationary environments, and captured robot policy execution with continuous-time Markov chains.
%
With these models, I have applied sequential decision making techniques, such as labelled real-time dynamic programming, to synthesise robust and efficient robot behaviour under uncertainty.
%
Moreover, I have used these models to develop a scalable discrete-event simulator which accurately captures task-level robot behaviour.
%
This simulator could be used within CONVINCE for rapid contingency planning during execution.
%
Formal model checking techniques can be utilised within CONVINCE to analyse why a robot has failed, and for execution monitoring.
%
Previously, I have utilised model checking techniques for continuous-time Markov chains, such as transient analysis, to reason over robot locations in continuous time, and the appearance of tasks in the environment.
%
If accepted for the role, I hope to translate some of these ideas to CONVINCE.

% Comms Skills
I have a strong publication record in high impact venues such as IEEE T-RO and AAMAS.
%
Further, I have presented my work at IEEE MRS and AAMAS, as well as through outreach events.
%
For example, at the 2021 Goodwood Festival of Speed, I led demonstrations of a Toyota Human Support Robot and UR10 Robotic Manipulator, and engaged with the public about robotics.
%
Moreover, I have supervised four undergraduate dissertations and two internships, preparing me for the increased responsibilities as a research fellow.
%
I have also led work on multi-robot warehouse logistics with industrial collaborators at Accenture Labs.

% Real Robot Deployment
In addition to research, I have integrated my work onto robotic systems using ROS.
%
In First Fleet, I integrated a planner developed during my DPhil onto agricultural robots supporting fruit pickers, which required modifications for online deployments.
%
My work with Team ORIon focused on deploying service robots in domestic environments.
%
This requires fundamental robot behaviours such as manipulation, perception, navigation, and speech to build an integrated robotic system.

% Closing statement
In summary, my research interests align well with the advertised role. 
%
If accepted I look forward to furthering my research as part of the CONVINCE project.

\end{document}