\documentclass[11pt]{article}
\usepackage[margin=65pt]{geometry}
\usepackage{multicol}
\usepackage[hidelinks]{hyperref}
\title{\vspace{-80pt}\underline{Charlie Street}}
\date{}
\hyphenation{Programme}%lets me remove hyphenation for specific words
\hyphenation{Computer}
\hyphenation{Programming}
\hyphenation{Computing}
\hyphenation{Operating}
\hyphenation{Birmingham}
\hyphenation{Waterloo}
\hyphenation{IntelliJam}
\begin{document}
	\pagenumbering{gobble}
	\maketitle
	\vspace*{-60pt}
	%\begin{flushleft}
	%	\noindent
	%	\large7 Cassiobury Road, Weymouth, Dorset. DT4 7JN\\                         %MAKE THIS LOOK NICER     
	%	\large 07917601977\\
     %     		 \large me@charliestreet.net
	%\end{flushleft}
	\begin{flushleft}
	\noindent
	\large 7 Cassiobury Road,
	\hfill
	\large 07917601977 \\
	\large Weymouth,
	\hfill 
	\large \href{mailto:me@charliestreet.net}{\nolinkurl{me@charliestreet.net}} \\
	\large Dorset. \\
	\large DT4 7JN. \\
	\end{flushleft}

	\vspace{-15pt}
	\begin{center}
			\textit{\large As a highly driven individual with a strong academic record, I throw myself into any challenge I am confronted with. With extra-curricular experience working in teams, I believe I can add value to any team-based project.}
	\end{center}
			
	\vspace{-30pt}
	\hspace{-100pt}\section*{\underline{Education}}
		\begin {itemize}
			\item \textbf{University (2014-2018)} Studying MSci Computer Science at the University of Birmingham.
				\begin{itemize}
					\item Achieved average grades of \textbf{94\%}, \textbf{95\%} and \textbf{89.5\%} in my first $3$ years respectively.
					\item Won Best in Degree Programme 2014/15, 2015/16 \& 2016/17.
					\item Won BCS Prize for Best in Year 2014/15.
					\item Won IBM Team Project Prize 2015/16.
					\item Awarded School of Computer Science Excellence Scholarship during first year.
					\item In April $2018$ I submitted my master's dissertation titled: `IntelliJam: An Intelligent Agent for Musical Improvisation'.
					\item Currently in my final (fourth) year.
					\item Completed modules in Intelligent Robotics, Machine Learning, Neural Computation, Operating Systems, Networks, Functional Programming and Computer Security among others.
				\end{itemize}
			\item \textbf{A Level (2012-2014)} Studied at the Thomas Hardye Sixth Form, Dorchester.
				\begin{itemize}
					\item Achieved an A* in A Level Maths, Physics and Computing and an A grade in AS Further Maths and Chemistry.
				\end{itemize}
			
		\end{itemize}
	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{Technical Skills}}
		\subsection*{\underline{Programming Languages}}
		\renewcommand{\arraystretch}{1.3}%
		\begin{tabular}[20pt]{ll}
			\textbf{C} & I have strong experience with memory management, pointers etc. \\
			\textbf{C++} & I can use classes and templates on top of the underlying C functionality. \\
			\textbf{Python} & I have familiarity with Python, having used it for Machine Learning/Robotics applications. \\
			\textbf{Haskell} & I have a reasonable understanding of Haskell and the functional paradigm.\\
			\textbf{Agda} & I can formulate inductive proofs over basic numbering systems and data structures.\\
			 \textbf{Java} &  I have a strong level of proficiency, having used Java heavily during my time at university.\\
			 \textbf{OCaml} & I have an understanding of the syntax and underlying concepts of the language.\\
			\textbf{JavaScript} &  I possess basic knowledge of the language to add functionality to web pages.\\
		\end{tabular} 
		\subsection*{\underline{Other}}
		\renewcommand{\arraystretch}{1.3}%
		\begin{tabular}{ll}
			 \textbf{Git} & I have experience using Git, having used it for any significant project I have partaken in.\\
			\textbf{LaTeX} & I've produced many documents in LaTeX, notably my dissertation.\\
			\textbf{Matlab} & I can use Matlab to carry out a variety of mathematical/graphical functions.\\
		\end{tabular}
	
	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{Projects}} %FINISH THIS AND CLEAN UP
			\begin{itemize}
				\item \textbf{IntelliJam (2017-2018)} The software created alongside my master's dissertation. IntelliJam uses Fractal Prediction Machines to allow a guitar player to play whilst connected to a computer and have an agent respond to their playing with new musical phrases in real time. In addition to the agent, a new method of melody extraction based on spectrogram filtering was devised.
				\item \textbf{Dating Chat-Bot for `The Gadget Show' (2016)} A project for the TV show to create a bot to partake in speed-dating. The goal was for an unknowing subject to choose the bot over a human. I led the back-end/AI sub-team; I was the majority contributor to the design and implementation of the bot. This forced me to think creatively while under time-pressure.
				\item \textbf{Simulizer (2016-2017)} A project initially undertaken for a second year module but continued since. Simulizer is a simulator and visualiser for a MIPS R3000 processor. Working in a team of 5, I was in charge of the back-end, requiring me to write a faithful simulation of the R3000 processor, including a primitive pipeline for execution. This has since been used as a significant teaching aid for the `Computer Systems \& Architecture' module at the University of Birmingham. Students had to write assignments in Simulizer; the assignments were graded using the software.
				\item \textbf{Pedalo (2017)} In September 2017 I was invited to Hack The North at the University of Waterloo, Canada's largest `hackathon'. While there, I was part of the team who created Pedalo, providing certificate verification on the Ethereum blockchain. Pedalo was awarded the `best use of blockchain' prize by ConsenSys. 
				\item \textbf{Hack The Midlands (2016/2017)} In 2016 I was placed 2nd at Hack The Midlands for creating DanceAuth: authentication via the user's dance moves. At the same event in 2017 I was placed 3rd for creating Vox: a system that makes an electric guitar `speak' using a text-to-speech engine.
			\end{itemize}

	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{Extra-Curricular Interests And Experiences}}
			\begin{itemize}
				\item \textbf{Music} I am an avid musician, having played the guitar since the age of 12 with interest in many musical genres. This has required great commitment and perseverance. Previously, I have been lead guitarist/backing vocalist for a rock covers band. Being an active member of a band has improved my ability to cooperate well within a group and listen to those around me. 
				\item \textbf{Duke Of Edinburgh Award} I've completed all 3 levels of the DofE award scheme. This required large amounts of team-work and communication, particularly during expeditions, which involved working in a team of 4 for 4 days on Dartmoor. This greatly benefit my leadership skills. I also partook in voluntary work including working in a local charity shop and aiding restoration work along a canal near Gloucester.
			\end{itemize}

				
	\vspace{-20pt}
	\hspace{-100pt}\section*{\underline{References}}	
				\begin{multicols}{2}
					\noindent
					Prof. Peter Tino:  \href{mailto:P.Tino@cs.bham.ac.uk}{\nolinkurl{P.Tino@cs.bham.ac.uk}}\\
					School of Computer Science,\\
					University of Birmingham,\\
					Birmingham, \\
					West Midlands.\\
					B15 2TT.\\
	
					\noindent
					Prof. Jeremy Wyatt: \href{mailto:J.L.Wyatt@cs.bham.ac.uk}{\nolinkurl{J.L.Wyatt@cs.bham.ac.uk}}\\
					School of Computer Science,\\
					University of Birmingham,\\
					Birmingham,\\
					West Midlands.\\
					B15 2TT.\\
				\end{multicols}


\end{document}
