\documentclass[12pt]{letter}
\usepackage{fullpage}
\usepackage{times}
\usepackage{hyperref}
\usepackage{url}

\signature{\vspace{-40pt} Charlie Street}
\address{\hfill Charlie Street \\ \hfill 56 Metchley Lane \\ \hfill Birmingham \\ \hfill B17 0HS \\ \hfill +44 7917601977 \\ \href{mailto:c.l.street@bham.ac.uk}{c.l.street@bham.ac.uk}}

\longindentation=0pt

\begin{document}

\begin{letter}{School of Computer Science \\ University of Birmingham \\ Birmingham \\ B15 2TT}
\opening{To whom it may concern,}


% PARA 1: Intro
I am writing to apply for the role of assistant professor in cyber-physical systems (4651).
%
As an internal applicant, I have years of experience in the school both as a member of staff and as a student.
%
I have been a research fellow in the school since January 2023, following the completion of my PhD at the University of Oxford in 2022.
%
My experience in research, teaching, leadership, and outreach have given me many of the skills required of an assistant professor.


% PARA 2: Research & Dissemination

% Come back to this bit last - describe my research at a very high level, what its goals are, and what are the key results thus far.
%
I am interested in the application of artificial intelligence techniques and formal verification to robotics.
%
The goal of my research is to develop robotic systems with a guaranteed quality of service under uncertainty.
%
My current research as part of EU Horizon project CONVINCE is focused on robot planning under spatiotemporal uncertainty.
%
For this, I apply sequential decision-making techniques to data-driven models of uncertainty.
%
The core achievment of my research so far has been techniques for multi-robot planning which apply model checking techniques to reason over the temporal behaviour of other robots and other exogenous processes in the environment.
%
My research has been published in high-quality venues such as IEEE Transactions on Robotics (T-RO), the Journal for Artificial Intelligence Research (JAIR), and the International Conference on Autonomous Agents and Multi-Agent Systems (AAMAS).
%
The applicability of my research has been demonstrated in external collaborations with the University of Lincoln for agricultural robotics, and Accenture Labs for hybrid order picking systems in warehouses.
%
Recently, I have also co-authored two grant proposals, one for an EU Horizon project, and one for a Google scholarship.
%
I am excited to continue with this research, and I believe an assistant professorship in the school of computer science provides me with an ideal opportunity to pursue it.

% PARA 3: Teaching
I am enthuastic to teach and supervise students.
%
Teaching is an important part of academic life which helps build a researcher through the development of communication and presentation skills.
%
I have already taught lectures for the Advanced Robotics course, and helped write the latest exam.
%
I have taught undergraduates how to write software for robots as part of Oxford's RoboCup team, and have worked as a teaching assistant on a robotics crash course for CDT students.
%
I also have supervision experience, having supervised numerous undergraduate, masters, and internship projects, and am currently on the supervision team for two PhD students.
%
I have also conributed to designing undergraduate projects.
%
I am excited to continue teaching and leading modules as an assistant professor.

% PARA 4: Leadership & Management
I've taken on leadership and management roles which will help me as an assistant professor.
%
I'm currently a technical work package lead in EU Horizon project CONVINCE.
%
As well as designing our own contributions, I collaborate with other packages, and manage our needs with theirs to help build a cohesive software toolchain.
%
During my PhD, I led the University of Oxford's RoboCup team, and led external collaborations with Accenture Labs.
%
I have also run a half-day tutorial on multi-robot planning at the 2023 International Conference on Autonomous Agents and Multi-Agent Systems (AAMAS).
%
I am comfortable in leadership positions, and can effectively manage tasks under tight deadlines.

% PARA 5: Citizenship
I am an active citizen of the school and hope to further this as assistant professor.
%
I have given multiple tours of our robot labs to students and members of the university's robotics society.
%
I've also engaged with regular events such as facts and snacks and social events.
%
I've also been recently involved in updating and reorganising the robotics labs.
%
I am keen to help with events such as open days and want to be a champion for the school.
%
I'm particularly interested in bringing a robotics presence to these events.
%
When I was applying for undergraduate study, seeing Bob being demonstrated in the building was a big part of why I wanted to study in Birmingham.
%
Its been a longstanding desire of mine to get Bob up and running again for similar events.


% PARA 6: Enterprise, Engagement and Impact/ Outreach
I have substantial experience in enterprise, engagement, and impact events.
%
My time leading Oxford's RoboCup team was focused on widening participation, recruiting students who had previously not had the opportunity to work in robotics.
%
I've led multiple robotics demos at public events, such as the Goodwood festival of speed, and University of Oxford open days.
%
I've also helped prepare robot demos for events at Blenheim palace, and for the opening of an Oxford college building visited by Prince William. 
%
I am passionate about outreach, and these events have taught me how to explain complex research in an accessible and entertaining way to members of the public.

% PARA 7: Summary and Thanks
Given my skills and prior experience, I am confident I can quickly adapt to the role of assistant professor.
%
To support this application, I include a research statement, teaching statement, and CV along with this cover letter.
%
Thank you for considering my application, and I look forward to hearing from you.


\closing{\vspace{40pt} Yours faithfully,}
\end{letter}
\end{document}
